---
title: "Baby Names"
documentclass: elsarticle
Thesis_FP: false
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: true
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Nico Katzke^[__Contributions:__  \newline _The authors would like to thank
  the World Happiness survey for showing us what happiness is._]
Ref1: Satrix, Cape Town
Email1: nfkatzke\@gmail.com
CorrespAuthor_1: true
BottomRFooter: \footnotesize Page \thepage
addtoprule: true
addfootrule: true
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: true
linenumbers: false
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: true
Journal: Journal of Finance
toc: false
numbersections: true
fontsize: 11pt
linestretch: 1.2
link-citations: true
AddTitle: true
abstract: |
  This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)

source("code/Data_Importing.R")
source("code/heatmap_function.R")
# Load data
data <- data_preparation(
  baby_names_path = "data/Baby_Names_By_US_State.rds",
  charts_path = "data/charts.rds",
  hbo_titles_path = "data/HBO_titles.rds",
  hbo_credits_path = "data/HBO_credits.rds"
)

# Extract the Baby_Names data frame from the list
Baby_Names <- data$Baby_Names
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

#Question 1:Baby Names

As requested this report first looks at the Spearman rank correlation, for each year's 25 most popular boys' and girls' names and that of the next 3 years. The graph is reported below:

```{r}
calculate_spearman_correlation(Baby_Names)
plot_spearman_correlation(correlations)
```
The correlation is given for 1 year up to 3 years and it shows that for both genders, the Spearman rank correlation tends to decrease as the lag increases. This means that the rankings of the top 25 names become less similar as the time interval between the compared years increases. The correlations for female names show variability over time but generally exhibit a decreasing trend as the lag increases. Similar to female names, male names also show a decreasing trend in correlation with increasing lag. Both genders show periods where the correlation drops significantly, which could indicate cultural or societal changes influencing baby name trends.The dips in the 3-year lag correlation suggest that names become less stable over longer periods, with new names gaining popularity while others fade.

\newpage
The study also looked to see what names over the period 1910 - 2014 were the most popular and mainstay names. The 25 most popular boys and girls names are given in the table below 
```{r}
generate_top_names_tables(top_25_names)# this creates the table 
```
As one can see Mary is the most popular girls name and James is the most popular boys name. The toy company would be wise to incorporate those names into character creation. The other popular names among the top 25 should also be seen as good candidates for character names.

\newpage
Lastly a heatmap is drawn which shows the popularity of 
```{r}
create_heatmap(Baby_Names)
```
The heatmap shows the change in popularity of names over time in the period the data was collected. It is interesting to note how certain names have fade completely away after a number of years. 
