---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Baby Names"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Nico Katzke^[__Contributions:__  \\newline _The authors would like to thank the World Happiness survey for showing us what happiness is._]"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "nfkatzke\\@gmail.com" # First Author's Email address

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)

source("code/Data_Importing.R")
source("code/heatmap_function.R")
# Load data
data <- data_preparation(
  baby_names_path = "data/Baby_Names_By_US_State.rds",
  charts_path = "data/charts.rds",
  hbo_titles_path = "data/HBO_titles.rds",
  hbo_credits_path = "data/HBO_credits.rds"
)

# Extract the Baby_Names data frame from the list
Baby_Names <- data$Baby_Names
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

#Question 1:Baby Names

As requested this report first looks at the Spearman rank correlation, for each year's 25 most popular boys' and girls' names and that of the next 3 years. The graph is reported below:

```{r}
calculate_spearman_correlation(Baby_Names)
plot_spearman_correlation(correlations)
```
The correlation is given for 1 year up to 3 years and it shows that for both genders, the Spearman rank correlation tends to decrease as the lag increases. This means that the rankings of the top 25 names become less similar as the time interval between the compared years increases. The correlations for female names show variability over time but generally exhibit a decreasing trend as the lag increases. Similar to female names, male names also show a decreasing trend in correlation with increasing lag. Both genders show periods where the correlation drops significantly, which could indicate cultural or societal changes influencing baby name trends.The dips in the 3-year lag correlation suggest that names become less stable over longer periods, with new names gaining popularity while others fade.

\newpage
The study also looked to see what names over the period 1910 - 2014 were the most popular and mainstay names. The 25 most popular boys and girls names are given in the table below 
```{r}
generate_top_names_tables(top_25_names)# this creates the table 
```
As one can see Mary is the most popular girls name and James is the most popular boys name. The toy company would be wise to incorporate those names into character creation. The other popular names among the top 25 should also be seen as good candidates for character names.

\newpage
Lastly a heatmap is drawn which shows the popularity of 
```{r}
create_heatmap(Baby_Names)
```
The heatmap shows the change in popularity of names over time in the period the data was collected. It is interesting to note how certain names have fade completely away after a number of years. 
