---
output:
  md_document:
    variant: markdown_github
---

# Purpose

Purpose of this work folder.

Ideally store a minimum working example data set in data folder.

Add binary files in bin, and closed R functions in code. Human Readable settings files (e.g. csv) should be placed in settings/


```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

#Explanation
Here I will explain my code, unfortunately things have gone horribly wrong I worked incorrectly admittedly. I worked in code folders and planned to move it over to readme's and functions and it went wrong but I will try to explain what my thinking was for each of question 1-4. In the hope of at least getting some marks. All my code was working until I tried putting into the readme and everything broke. The .rmd file did not want to knit either. 

#Question 1


```{r}
#Data Importing

data_preparation <- function(baby_names_path, charts_path, hbo_titles_path, hbo_credits_path) {
    library(dplyr)
    library(readr)
    library(janitor)

    Baby_Names <- read_rds(baby_names_path) %>% clean_names()
    charts <- read_rds(charts_path)
    HBO_Titles <- read_rds(hbo_titles_path)
    HBO_Credits <- read_rds(hbo_credits_path)

    return(list(Baby_Names = Baby_Names, charts = charts, HBO_Titles = HBO_Titles, HBO_Credits = HBO_Credits))
}

```

With this code I wanted to upload the data using read_rds to read in the data and store it in a tibble. The data was stored in the data file.

```{r}
#Spearman rank correlation

calculate_spearman_correlation <- function(Baby_Names) {
    library(dplyr)

    # Function to get top 25 names for each gender and year
    get_top_names <- function(data, year, gender) {
        data %>%
            filter(year == !!year, gender == !!gender) %>%
            top_n(25, wt = count) %>%
            arrange(desc(count))
    }

    # Get top 25 names by year and gender
    top_names_by_year <- Baby_Names %>%
        group_by(year, gender) %>%
        do(get_top_names(., .$year[1], .$gender[1])) %>%
        ungroup()

    # Function to calculate Spearman correlation for a given year and gender
    calculate_spearman <- function(year, gender) {
        current_year_names <- top_names_by_year %>%
            filter(year == !!year, gender == !!gender) %>%
            select(name)

        correlations <- sapply(1:3, function(offset) {
            next_year_names <- top_names_by_year %>%
                filter(year == !!(year + offset), gender == !!gender) %>%
                select(name)

            common_names <- intersect(current_year_names$name, next_year_names$name)

            if (length(common_names) < 2) return(NA)

            current_ranks <- match(common_names, current_year_names$name)
            next_ranks <- match(common_names, next_year_names$name)

            cor(current_ranks, next_ranks, method = "spearman")
        })

        data.frame(
            year = year,
            gender = gender,
            cor_1_year = correlations[1],
            cor_2_year = correlations[2],
            cor_3_year = correlations[3]
        )
    }

    # Apply the function across years and genders
    correlations <- Baby_Names %>%
        filter(year >= 1910 & year <= 2011) %>%
        distinct(year, gender) %>%
        rowwise() %>%
        do(calculate_spearman(.$year, .$gender)) %>%
        ungroup()

    return(correlations)
}
```

This Code was to calculate the spearman correlations for every year, up to three years

```{r}
#Spearman Plot function

plot_spearman_correlation <- function(correlations, title = "Spearman Rank Correlation of Baby Names Over Time", subtitle = "Comparing each year’s top 25 names with the next 3 years", base_size = 15) {
    library(ggplot2)
    library(tidyr)

    # Prepare the data for plotting
    correlations_long <- correlations %>%
        gather(key = "lag", value = "correlation", starts_with("cor_"))

    # Plot the correlations
    ggplot(correlations_long, aes(x = year, y = correlation, color = lag)) +
        geom_line(size = 1) +
        facet_grid(gender ~ lag, scales = "free_y") +
        scale_color_manual(values = c("cor_1_year" = "#1f77b4", "cor_2_year" = "#ff7f0e", "cor_3_year" = "#2ca02c"),
                           labels = c("1 year", "2 years", "3 years")) +
        labs(
            title = title,
            subtitle = subtitle,
            x = "Year",
            y = "Spearman Rank Correlation",
            color = "Comparison with"
        ) +
        theme_minimal(base_size = base_size) +
        theme(
            plot.title = element_text(hjust = 0.5, face = "bold"),
            plot.subtitle = element_text(hjust = 0.5),
            legend.position = "bottom",
            legend.title = element_text(face = "bold"),
            legend.background = element_rect(fill = "lightgray", size = 0.5, linetype = "solid", color = "darkgray")
        )
}
```
This graphs the Spearman rank correlation, facet_grid splits each of the series from lag(1) to lag(3) for the top 25 male and female names. 

```{r}
#Generate table of top boy and girls name
generate_top_names_tables <- function(top_25_names) {
    library(dplyr)
    library(gt)
    library(scales)

    # Split into boys' and girls' tables
    top_25_girls <- top_25_names %>%
        filter(gender == "F") %>%
        select(-gender) %>%
        arrange(desc(total_count))

    top_25_boys <- top_25_names %>%
        filter(gender == "M") %>%
        select(-gender) %>%
        arrange(desc(total_count))

    # Create a gt table for girls
    girls_table <- top_25_girls %>%
        gt() %>%
        tab_header(
            title = "Top 25 Most Popular Girls' Names (1910-2014)",
            subtitle = "Based on total count across all US states"
        ) %>%
        cols_label(
            name = "Name",
            total_count = "Total Count"
        ) %>%
        fmt_number(
            columns = vars(total_count),
            sep_mark = ",",
            decimals = 0
        ) %>%
        data_color(
            columns = vars(total_count),
            colors = scales::col_numeric(
                palette = c("white", "pink"),
                domain = NULL
            )
        )

    # Create a gt table for boys
    boys_table <- top_25_boys %>%
        gt() %>%
        tab_header(
            title = "Top 25 Most Popular Boys' Names (1910-2014)",
            subtitle = "Based on total count across all US states"
        ) %>%
        cols_label(
            name = "Name",
            total_count = "Total Count"
        ) %>%
        fmt_number(
            columns = vars(total_count),
            sep_mark = ",",
            decimals = 0
        ) %>%
        data_color(
            columns = vars(total_count),
            colors = scales::col_numeric(
                palette = c("white", "lightblue"),
                domain = NULL
            )
        )

    return(list(girls_table = girls_table, boys_table = boys_table))
}
```
This code takes the top 25 names average over the period and prints them in a nice table. The Idea was to see which names remained popular over the whole period

```{r}
#Heatmap_function
create_heatmap <- function(Baby_Names, start_year = 1910, end_year = 2014, top_n = 25, base_size = 12) {
    library(dplyr)
    library(ggplot2)

    # Function to get top 25 names for each gender and year
    get_top_names <- function(data, year, gender) {
        data %>%
            filter(year == !!year, gender == !!gender) %>%
            top_n(top_n, wt = count) %>%
            arrange(desc(count))
    }

    # Get top names by year and gender
    top_names_by_year <- Baby_Names %>%
        filter(year >= start_year & year <= end_year) %>%
        group_by(year, gender) %>%
        do(get_top_names(., .$year[1], .$gender[1])) %>%
        ungroup()

    # Prepare data for heatmap
    heatmap_data <- top_names_by_year %>%
        mutate(name = factor(name, levels = unique(name))) %>%
        select(year, name, count, gender)

    # Create the heatmap
    ggplot(heatmap_data, aes(x = name, y = year, fill = count)) +
        geom_tile(color = "white") +
        scale_fill_gradient(low = "white", high = "blue", name = "Count") +
        labs(
            title = "Top 25 Most Popular Baby Names",
            subtitle = paste("Color intensity represents the count of the names from", start_year, "to", end_year),
            x = "Name",
            y = "Year"
        ) +
        facet_wrap(~ gender, scales = "free_x", ncol = 1) +
        theme_minimal(base_size = base_size) +
        theme(
            axis.text.x = element_text(angle = 45, hjust = 1),
            plot.title = element_text(hjust = 0.5, face = "bold"),
            plot.subtitle = element_text(hjust = 0.5)
        )
}


```

This is the function for the heatmap, the Idea was for the heatmap to measure popularity of names over the years and how it faded away or became popular. facet_wrap is used to split on gender. fill = count is used to show how many people had a specific name in a year.

#Question 2

```{r}
clean_music_data <- function(coldplay_path = "data/Coldplay.csv", metallica_path = "data/metallica.csv") {
    library(dplyr)
    library(readr)

    # Read the data
    coldplay <- read_csv(coldplay_path)
    metallica <- read_csv(metallica_path)

    # Remove live performances from Coldplay
    clean_coldplay <- coldplay %>% filter(!grepl("live", name, ignore.case = TRUE))

    # Remove live performances and other issue entries from Metallica
    clean_metallica <- metallica %>%
        filter(!grepl("live", name, ignore.case = TRUE)) %>%
        filter(!grepl("Demo", name, ignore.case = TRUE)) %>%
        filter(!grepl("Writing in Progress", name, ignore.case = TRUE)) %>%
        filter(!grepl("Remastered", name, ignore.case = TRUE)) %>%
        filter(!grepl("Tapes", name, ignore.case = TRUE)) %>%
        filter(!grepl("Rehearsal", name, ignore.case = TRUE)) %>%
        filter(!grepl("(Work in Progress Rough Mix)", name, ignore.case = TRUE)) %>%
        filter(!grepl("Radio Edit", name, ignore.case = TRUE)) %>%
        filter(!grepl("Rough Mix", name, ignore.case = TRUE)) %>%
        filter(!grepl("Edit", name, ignore.case = TRUE)) %>%
        filter(!grepl("Remastered", album, ignore.case = TRUE)) %>%
        filter(!grepl("Remaster", album, ignore.case = TRUE)) %>%
        filter(!grepl("Some Kind Of Monster (Live)", album, ignore.case = TRUE)) %>%
        filter(!grepl("Garage, Inc.", album, ignore.case = TRUE))

    return(list(clean_coldplay = clean_coldplay, clean_metallica = clean_metallica))
}
```
This imports the data and cleans it. grepl was used to remove any instance of metallica songs that was not studio recorded. The same was done for ColdPlay albeit it was a bit easier.

```{r}
create_popularity_plots <- function(clean_coldplay, clean_metallica) {
    library(ggplot2)

    # Coldplay popularity by album
    popularity_plot_coldplay <- clean_coldplay %>%
        ggplot() +
        geom_boxplot(aes(album_name, popularity, fill = album_name)) +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        labs(
            title = "Popularity by album: Coldplay",
            x = "Album name",
            y = "Popularity",
            fill = "Album name"
        )

    # Metallica popularity by album
    popularity_plot_metallica <- clean_metallica %>%
        ggplot() +
        geom_boxplot(aes(album, popularity, fill = album)) +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        labs(
            title = "Popularity by album: Metallica",
            x = "Album name",
            y = "Popularity",
            fill = "Album name"
        )

    return(list(coldplay_plot = popularity_plot_coldplay, metallica_plot = popularity_plot_metallica))
}
```

This draws the popularity plot, I did the box plot as that was the one shown for Metallica. I did it for ColdPlay as well. Text angle was changed to 90 degrees so there is no overlap.

```{r}
create_bar_plot <- function(clean_coldplay, clean_metallica) {
    library(dplyr)
    library(ggplot2)
    library(scales)  # for rescale function
    library(tidyr)

    # Rename and mutate columns as necessary
    clean_coldplay <- clean_coldplay %>% rename(album = album_name)
    clean_metallica <- clean_metallica %>% mutate(duration = duration_ms / 1000) %>% rename(duration = duration_ms)
    clean_coldplay <- clean_coldplay %>% mutate(artist = "Coldplay")
    clean_metallica <- clean_metallica %>% mutate(artist = "Metallica")

    # Combine the datasets
    coldplay_metallica <- bind_rows(clean_coldplay, clean_metallica)

    # Prepare the data for the bar plot
    bar_data <- coldplay_metallica %>%
        select(artist, album, acousticness, danceability, energy, instrumentalness, liveness, loudness, speechiness, tempo, valence) %>%
        group_by(artist, album) %>%
        summarise(across(everything(), mean, na.rm = TRUE))

    # Normalize the data to bring all metrics to the same scale (0 to 1)
    bar_data_normalized <- bar_data %>%
        mutate(across(acousticness:valence, ~ rescale(.x, to = c(0, 1))))

    # Transform data to long format for plotting using gather
    bar_data_long <- bar_data_normalized %>%
        gather(key = "metric", value = "value", -artist, -album)

    # Create faceted bar plot
    bar_plot <- ggplot(bar_data_long, aes(x = album, y = value, fill = artist)) +
        geom_bar(stat = "identity", position = "dodge") +
        facet_wrap(~ metric, scales = "free_y", ncol = 3) +
        scale_fill_manual(values = c("Coldplay" = "blue", "Metallica" = "red")) +
        labs(
            title = "Comparison of Coldplay and Metallica Across Various Metrics by Album",
            subtitle = "Normalized mean values of musical characteristics",
            x = "Album",
            y = "Normalized Value"
        ) +
        theme_minimal(base_size = 14) +
        theme(
            plot.title = element_text(hjust = 0.5, face = "bold"),
            plot.subtitle = element_text(hjust = 0.5),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "bottom"
        )

    return(bar_plot)
}
```
This creates a bar plot to compare albums in terms of the metrics given such as valence. I took averages so that of songs within the album of both Metallica and Coldplay and produce a barplot for each. Again the data was first cleaned so that rowbind could be used to merge the data. A variable was also created to track whether it was Metallica or ColdPLay. 

#Question 3

```{r}
process_data <- function(alloc,commit) {
    library(tidyverse)
    library(janitor)

    # Reading in the data
    alloc <- read_csv("data/Finanicial Allocations.csv")
    commit <- read_csv("data/Financial Commitments.csv")

    # Joining the two datasets for analysis
    alloc_plus_commit <- left_join(commit, alloc, by = c("Country", "EU member")) %>% clean_names()

    # Reorder the country factor based on eu_member
    alloc_plus_commit <- alloc_plus_commit %>%
        mutate(country = factor(country, levels = country[order(eu_member, decreasing = TRUE)]))

    return(alloc_plus_commit)
}
```
Again the data is read in and cleaned, the names of the columns are made more suitable for r using clean_names() to augment it.

```{r}
plot_commitment_data <- function(alloc_plus_commit) {
    library(dplyr)
    library(tidyr)
    library(ggplot2)

    # Transform the data
    commit_long <- alloc_plus_commit %>%
        select(country, eu_member, gdp_in_2021_billion, financial_commitments_billion, humanitarian_commitments_billion, military_commitments_billion) %>%
        gather(key = "commitment_type", value = "amount_billion",
               financial_commitments_billion, humanitarian_commitments_billion, military_commitments_billion)

    # Create the plot
    plot <- commit_long %>%
        filter(country != "EU (Commission and Council)") %>%
        group_by(eu_member) %>%
        ggplot(aes(x = country, y = amount_billion, fill = commitment_type)) +
        geom_bar(stat = "identity", position = "stack") +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        labs(
            title = "Aid Commitment By Type",
            subtitle = "All countries to the left of Australia are EU members",
            x = "Country",
            y = "Total Bilateral Commitments (Billion)",
            fill = "Commitment Type"
        )

    return(plot)
}
```
This function plots the amount committed towards Ukraine while splitting on whether it was humanitarian, financial or military aid. Position = "stack" allows for the bars to be coloured differently depending on the amount of the types of aid.

```{r}
plot_allocation_data <- function(alloc_plus_commit) {
    library(dplyr)
    library(tidyr)
    library(ggplot2)

    # Transform the data
    alloc_long <- alloc_plus_commit %>%
        select(country, eu_member, gdp_in_2021_billion, financial_allocations_billion, humanitarian_allocations_billion, military_allocations_billion) %>%
        gather(key = "allocation_type", value = "amount_billion",
               financial_allocations_billion, humanitarian_allocations_billion, military_allocations_billion)

    # Create the plot
    plot <- alloc_long %>%
        filter(country != "EU (Commission and Council)") %>%
        group_by(eu_member) %>%
        ggplot(aes(x = country, y = amount_billion, fill = allocation_type)) +
        geom_bar(stat = "identity", position = "stack") +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        labs(
            title = "Aid Allocation By Type",
            subtitle = "All countries to the left of Australia are EU members",
            x = "Country",
            y = "Total Bilateral Allocations (Billion)",
            fill = "Allocation Type"
        )

    return(plot)
}
```

This function does the exact same as above but this is for the allocation. Also all EU members are to the left of Australia.

#Question 4

```{r}
#reading in olympic data
process_olympics_data <- function(gdp_path, summer_path, winter_path) {
    library(tidyverse)
    library(janitor)

    # Read the datasets
    gdp <- read_rds(gdp_path) %>% clean_names()
    summer <- read_rds(summer_path) %>% clean_names()
    winter <- read_rds(winter_path) %>% clean_names()

    # Add Olympics type
    summer <- summer %>% mutate(olympics = "Summer")
    winter <- winter %>% mutate(olympics = "Winter")

    # Bind the summer and winter Olympics datasets
    sw_oly <- bind_rows(summer, winter)

    # Join with GDP data
    sw_gdp <- left_join(sw_oly, gdp, by = c("country" = "code")) %>%
        select(-country) %>%
        rename(country = country.y)

    # Join summer Olympics with GDP data and clean the result
    summer_gdp <- left_join(summer, gdp, by = c("country" = "code"))
    summer_gdp_cleaned <- summer_gdp %>%
        select(-country) %>%
        rename(country = country.y)

    return(list(sw_gdp = sw_gdp, summer_gdp_cleaned = summer_gdp_cleaned))
}
```
Again some data wrangling to join all 3 data sets. Summer and Winter Olympics could just be row binded since they have the same columns. A variable was just created to keep track of whether it was Winter or Summer olympics.

```{r}
#Plotting India's performance relative to other emerging market economies
analyze_medals_gdp <- function(data, target_country = "India", gdp_threshold = 0.5) {
    library(dplyr)
    library(ggplot2)

    # Calculate mean GDP per capita for the target country
    target_gdp_per_capita <- data %>%
        filter(country == target_country) %>%
        summarize(mean_gdp_per_capita = mean(gdp_per_capita, na.rm = TRUE)) %>%
        pull(mean_gdp_per_capita)

    # Inspect the distribution of GDP per capita for all countries
    gdp_distribution <- data %>%
        group_by(country) %>%
        summarize(mean_gdp_per_capita = mean(gdp_per_capita, na.rm = TRUE)) %>%
        arrange(mean_gdp_per_capita)

    # Find countries with similar GDP per capita
    similar_countries <- data %>%
        filter(gdp_per_capita >= (target_gdp_per_capita * (1 - gdp_threshold)) &
                   gdp_per_capita <= (target_gdp_per_capita * (1 + gdp_threshold))) %>%
        pull(country) %>%
        unique()

    # Filter the data for the target country and similar economies
    filtered_data <- data %>%
        filter(country %in% c(target_country, similar_countries))

    # Ensure team sport medals are counted as one medal
    team_medals <- filtered_data %>%
        distinct(year, city, sport, discipline, event, medal, country, gdp_per_capita)

    # Summarize the medal counts for the target country and similar economies
    medal_counts <- team_medals %>%
        filter(medal %in% c("Gold", "Silver", "Bronze")) %>%
        group_by(country, medal) %>%
        summarize(medal_count = n()) %>%
        ungroup()

    # Add total medals count for each country
    total_medals <- medal_counts %>%
        group_by(country) %>%
        summarize(total_medals = sum(medal_count))

    # Merge the data
    medal_summary <- medal_counts %>%
        left_join(total_medals, by = "country") %>%
        arrange(desc(total_medals))

    # Get the GDP per capita for each country
    gdp_per_capita_summary <- team_medals %>%
        group_by(country) %>%
        summarize(mean_gdp_per_capita = mean(gdp_per_capita, na.rm = TRUE))

    # Merge gdp_per_capita_summary with medal_summary to get the GDP per capita for each country
    medal_summary <- medal_summary %>%
        left_join(gdp_per_capita_summary, by = "country")

    # Define custom colors for medals
    medal_colors <- c("Gold" = "#FFD700", "Silver" = "#C0C0C0", "Bronze" = "#CD7F32")

    # Create the plot
    plot <- ggplot(medal_summary, aes(x = reorder(country, total_medals), y = medal_count, fill = medal)) +
        geom_col() +
        geom_text(aes(label = medal_count), position = position_stack(vjust = 0.5), color = "black") +
        geom_text(aes(x = reorder(country, total_medals), y = total_medals, label = round(mean_gdp_per_capita, 2)),
                  vjust = 0.5, hjust = -0.1, size = 5, color = "black") +
        scale_fill_manual(values = medal_colors) +
        coord_flip() +
        labs(title = "Medal Count Comparison: India vs. Similarly Sized Economies",
             subtitle = "GDP per capita for each country is printed to the right of each column",
             x = "Country",
             y = "Medal Count") +
        theme_minimal()

    return(plot)
}

```
This function looks at India's GDP and then takes countries with similar GDP to India and compares the amount of medals won while also accounting for whether it was a team event taking those medals as 1. the geom_col() also accounts for the number of bronze silver and gold medals won.

```{r}
plot_medal_counts_over_time <- function(data) {
    library(dplyr)
    library(ggplot2)

    # Summarize medal counts by year, country, and Olympics type
    medal_counts <- data %>%
        filter(medal %in% c("Gold", "Silver", "Bronze")) %>%
        group_by(year, country, olympics) %>%
        summarize(medal_count = n()) %>%
        ungroup()

    # Select a few countries to visualize
    selected_countries <- c("United States", "South Africa", "Germany", "United Kingdom", "Norway", "China")

    # Filter the data for the selected countries
    filtered_data <- medal_counts %>%
        filter(country %in% selected_countries)

    # Plot the time-series analysis side-by-side for selected countries
    ggplot(filtered_data, aes(x = year, y = medal_count, color = olympics, group = olympics)) +
        geom_line() +
        facet_wrap(~ country, scales = "free_y") +
        labs(title = "Medals Won Over Time in Selected Countries",
             subtitle = "Comparing dominance in Winter and Summer Olympics",
             x = "Year",
             y = "Number of Medals",
             color = "Olympics") +
        theme_minimal()
}
```
This plots a line plot over time of the amount of medals won over the years by a selected group of countries.

```{r}
plot_medals_vs_gdp <- function(data) {
    library(dplyr)
    library(ggplot2)
    library(countrycode)

    # Create a continent variable
    data <- data %>%
        mutate(continent = countrycode(sourcevar = country, origin = "country.name", destination = "continent"))

    # Summarize the number of medals won by each country
    medal_summary <- data %>%
        group_by(country, continent, gdp_per_capita, population) %>%
        summarize(total_medals = n(), .groups = 'drop')

    # Remove rows with non-finite values
    medal_summary <- medal_summary %>%
        filter(is.finite(gdp_per_capita) & is.finite(total_medals) & is.finite(population))

    # Calculate medals per population
    medal_summary <- medal_summary %>%
        mutate(medals_per_population = total_medals / population)

    # Identify the top 5 countries by medals per population
    top5_countries <- medal_summary %>%
        arrange(desc(medals_per_population)) %>%
        slice(1:5)

    # Create the point plot with continent colors and enhanced aesthetics
    ggplot(medal_summary, aes(x = gdp_per_capita, y = total_medals, size = population, color = continent)) +
        geom_point(alpha = 0.7) +
        geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed", aes(group = 1)) +  # Add regression line with grouping
        geom_text(data = top5_countries, aes(label = country), vjust = -1, size = 5) +  # Add country labels for top 5
        scale_size_continuous(name = "Population", range = c(3, 12)) +  # Adjust point size range
        scale_x_continuous(labels = scales::dollar) +  # Format x-axis labels as dollars
        scale_y_continuous(labels = scales::comma) +  # Format y-axis labels with commas
        labs(title = "Medals Won by GDP per Capita",
             subtitle = "The 5 labeled countries perform best relative to their population size.",
             x = "GDP per Capita",
             y = "Total Medals",
             caption = "Note: The size of the bubble represents the population size.",
             color = "Continent") +
        theme_minimal() +
        theme(
            legend.position = "bottom",
            legend.box = "horizontal",
            plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
            plot.subtitle = element_text(size = 14, hjust = 0.5),
            axis.title = element_text(size = 14, face = "bold"),
            axis.text = element_text(size = 12)
        )
}
```
This creates a point plot that checks the amount of medals won measured against GDP per Capita. A continent variable was created so that the bubbles were coloured with respect to there continent 

```{r}
#Medal for badminton per country
plot_badminton_medals <- function(data) {
    library(dplyr)
    library(ggplot2)

    # Filter data for Badminton
    badmin_data <- data %>% filter(discipline == "Badminton")

    # Summarize medal counts by country for Badminton
    top_countries <- badmin_data %>%
        group_by(country) %>%
        summarize(total_medals = n()) %>%
        arrange(desc(total_medals)) %>%
        head(10)

    # Plot top countries by medals
    ggplot(top_countries, aes(x = reorder(country, total_medals), y = total_medals, fill = country)) +
        geom_bar(stat = "identity") +
        coord_flip() +
        labs(title = "Top 10 Countries by Badminton Medals",
             x = "Country",
             y = "Total Medals",
             fill = "Country") +
        theme_minimal()
}
```

This function just plots the amount of medals won in badminton by the top 10 different countries. A bar plot was used to show this and coord_flip() was used to flip the bar around. reorder() is used to order the countries from by most medals to least medals. 